Personality and political beliefs across the lifespan

### 2019-11-20 scripts/manuscript.Rmd
messy data (pivot_wider)
Utilized pivot_wider() to expand types of conservatism and personality traits across columns

```{r figure2}
ggplot(tidy, aes(x = age, y = conservatism_score, color = conservatism_type)) +
  geom_smooth(se=FALSE, method = "lm")+
  labs(title = "Conservatism across the lifespan (adults aged 20-68)", subtitle = "Difference in Economic and Social Conservatism by Gender",
       x= "Age", y = "Conservatism Score (higher = more conservative)",
       color = "Conservatism Type")+
  theme_minimal()+
  facet_wrap(~gender)

@@

```{r}

>>>>

```{r figure2}
ggplot(tidy, aes(x = age, y = conservatism_score, color = conservatism_type)) +
  geom_smooth(se=FALSE, method = "lm")+
  scale_color_viridis_d() +
  labs(title = "Conservatism across the lifespan (adults aged 20-68)", subtitle = "Difference in Economic and Social Conservatism by Gender",
       x= "Age", y = "Conservatism Score (higher = more conservative)",
       color = "Conservatism Type")+
  theme_minimal()+
  facet_wrap(~gender)

@@

```{r messy_data}
messy <- tidy %>% 
  pivot_wider(
    names_from = conservatism_type, 
    values_from = conservatism_score) %>%
   pivot_wider(
     names_from = personality_trait,
     values_from = personality_score)
